Size-differentiated Export in Different Dynamical Regimes in the Ocean

### 2019-08-28 size_differentiated_export.tex
attempt to fix an issue

In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}). During this time, the Total Kinetic Energy (KE$_{\text{tot}}$) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation. The flattening of the KE$_{\text{tot}}$ curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments. The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where $f$ = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).

@@

\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}. At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \citep[Figure \ref{fig: Papa_winter}][]{Pelland_2016}. After spin-up, the vertical stratification remains consistent throughout the model run, and compares well with the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}). In the horizontal, prescribed density fronts are much sharper than in summer (i.e., over smaller spatial scales O(1 km ) vs. O(10 km)). Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in summer (Figure \ref{fig: Papa_winter}). As a result, KE$_{\text{tot}}$ starts to plateau at doy 48. The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized.

>>>>

In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}). During this time, the Total Kinetic Energy (KE$_$tot) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation. The flattening of the KE$_$tot curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments. The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where $f$ = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).

@@

\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}. At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \citep[Figure \ref{fig: Papa_winter}][]{Pelland_2016}. After spin-up, the vertical stratification remains consistent throughout the model run, and compares well with the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}). In the horizontal, prescribed density fronts are much sharper than in summer (i.e., over smaller spatial scales O(1 km ) vs. O(10 km)). Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in summer (Figure \ref{fig: Papa_winter}). As a result, KE$_$tot starts to plateau at doy 48. The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized.
